Figure 1 - overview

### 2024-07-15 ms_figure_1_overview.Rmd
Indicate meiosis-specific TFs in SuppFig1 with color

cowplot::plot_grid(
    gg_tpm + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) + 
        labs(x = "") + geom_point(size = 3), 
    gg_nbrint_all,
    gg_nbrpeaks_all_wide,
    ncol = 1, 
    align = "v", 
    axis = "l",
    labels = c("A", "B", "C"),
    rel_heights = c(1, 1, 1)
)
```

>>>>

cowplot::plot_grid(
    gg_tpm + theme(axis.text.x = element_blank(),
                   axis.ticks.length.x = unit(4, "mm"),
                   axis.ticks.x = element_line(color = main_colors[1],
                                               linewidth = 2.25)) +
        labs(x = "") + geom_point(size = 3), 
    gg_nbrint_all,
    gg_nbrpeaks_all_wide,
    ncol = 1, 
    align = "v", 
    axis = "l",
    labels = c("A", "B", "C"),
    rel_heights = c(1, 1, 1)
)
```
